Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-06-08 SIR_manuscript.tex
added 1 ref

In this paper, we have defined and analyzed a simple compartmental model that combines epidemiological dynamics (as defined by a simple SIR model) with the dynamics of testing and isolation. Our model is a caricature --- it models the most basic feedbacks between epidemic and testing processes, but does not attempt to incorporate the many known complications of COVID-19 epidemiology (e.g. exposed, presymptomatic, and asymptomatic compartments [REFS]; time-varying testing rates [REFS?]; behavioural dynamics [REF Weitz/Park/Dushoff]). Thus, it is most appropriate for assessing the \emph{qualitative} phenomena that arise from the interactions between epidemiology and testing, rather than for making quantitative predictions or guiding pandemic responses.

>>>>

In this paper, we have defined and analyzed a simple compartmental model that combines epidemiological dynamics (as defined by a simple SIR model) with the dynamics of testing and isolation. Our model is a caricature --- it models the most basic feedbacks between epidemic and testing processes, but does not attempt to incorporate the many known complications of COVID-19 epidemiology (e.g. exposed, presymptomatic, and asymptomatic compartments [REFS]\ali{\citep{kain2021chopping} OK?}; time-varying testing rates [REFS?]\ali{\citep{jarvis2021temporal} OK?}; behavioural dynamics [REF Weitz/Park/Dushoff] \ali{\citep{weitz2020awareness} OK?}). Thus, it is most appropriate for assessing the \emph{qualitative} phenomena that arise from the interactions between epidemiology and testing, rather than for making quantitative predictions or guiding pandemic responses.
